Allowing Stable Groups of Prosumers to Enter the Market through Proper Aggregation

### 2014-09-11 Article.tex
update

There seems to have a clear consensus on the benefit of having a bidirectional communication flows between prosumers and the grid as most of the demand side management concepts have proposed \cite{WuHamedHuangBook2011}. Nevertheless as the number of active prosumers is expected to rise, it is safe to assume there is a need for more complex communication pattern (such as coalitions) that will help to decrease the communication burden and in the mean time satisfy the multiple requirements of the power grid management. The formation of coalition inside the smart grid environment could be applied to various agents such as the self sufficient micro-grids\cite{Pahwa}, the virtual power plants (VPP), sizable and adjustable plants \cite{Braun} \cite{Ramchurn}, or fleet of electric vehicles that back up the grid in some emergency situations (V2G) \cite{Ramchurn}, are just a few use case where the coalition of multiple agents can enhance grid reliability and in the mean time reduce the communication burden.

>>>>

There seems to have a clear consensus on the benefit of having a bidirectional communication flows between prosumers and the grid as most of the demand side management concepts have proposed \cite{WuHamedHuangBook2011}. Nevertheless as the number of active prosumers is expected to rise, it is safe to assume there is a need for more complex communication pattern (such as coalitions) that will help to decrease the communication burden and in the mean time satisfy the multiple requirements of the power grid management. The formation of coalition inside the smart grid environment could be applied to various type of agent such as the self sufficient micro-grids\cite{Pahwa}, the virtual power plants (VPP), sizable and adjustable plants \cite{Braun} \cite{Ramchurn}, or fleet of electric vehicles that back up the grid in some emergency situations (V2G) \cite{Ramchurn}, are just a few use case where the coalition of multiple agents can enhance the grid reliability and in the mean time reduce the communication burden.
